Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-04-24 paper/article_jos.qmd
update plots + articles

:::: {.abstract}
This paper studies and compares real-time estimates of the trend-cycle component with moving averages based on local polynomial regression.
In particular, this theory allows us to reproduce Henderson's symmetric and Musgrave's asymmetric filters.
This paper describes how they can be extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parametrised globally, which can be suboptimal around turning points, this paper proposes a procedure for parametrising them locally.
An empirical comparison, based on simulated and real data, shows that modelling polynomial trends that are too complex introduces more revisions without reducing the phase shift, and that local parametrisation reduces the delay in detecting turning points and reduces revisions.
The paper also shows how these results can be easily reproduced using the R package `rjd3filters` dedicated to the manipulation of moving averages.

@@

Using local polynomial regression, @proietti2008 developed a general class of symmetric and asymmetric moving averages.
In particular, it becomes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
However, these methods have two drawbacks.
Firstly, the phase shift (i.e. the delay in detecting turning points) is not directly controlled.
Secondly, asymmetric filters depend on a parameter that is generally estimated over the whole series using assumptions that may be wrong locally.
The aim of this study is to propose extensions to the @proietti2008 class of filters in order to take these shortcomings into account.
Those extensions are implemented in the statistical software R [@logicielr] throw the `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and can therefore be easily used.
All the code associated to this paper is available at <https://github.com/XXXX> (anonymized linked before the manuscript is accepted).

@@

The basic assumption  used in  time series decomposition methods is that the input observed time series, $y_t$ can be decomposed into a signal component $g_t$ and a an erratic component $\varepsilon_t$ (called irregular):
$$
f(y_t)=g_t+\varepsilon_t
$$
where $f$ denotes some appropriate transformation (usually logarithmic or no transformation).
To simplify further notations, $y_t$ will denote the transformed observed series.
The noise component $\varepsilon_t$ is usually assumed to be a white noise.
Assuming that the input time series is seasonally adjusted (or without seasonality), the signal $g_t$ represents the trend and cycle components, here estimated jointly and called trend-cycle $TC_t$.
This component can be locally approximated by a polynomial degree (see @sec-nonparamreg):
$$
g_t = \sum_{j=0}^d\beta_jt^j+\xi_t
$$
with $\xi_t$ a stochastic process uncorrelated with $\varepsilon_t$.
Event if some papers model $\xi_t$ and $\varepsilon_t$ separately [see for example @GrayThomson2002], an usual assumption, adopted in this paper, is to is to gather $\xi_t$ and $\varepsilon_t$.
Thus, the trend-cycle $TC_t$ is considered as deterministic and modelled as a polynomial trend of degree $d$.
The coefficients $(\beta_0,\dots,\beta_k)$ can be estimated by weighted least squares.
The estimate $\hat \beta_0$ provides the trend-cycle estimate $\hat TC_t$ and it can be shown that this equivalent to apply of moving average (see @sec-nonparamreg).

@@

Fourier decomposition allows us to analyze any time series as a sum of harmonic series, and each component (trend, cycle, seasonal, irregular) is associated with a set of frequencies.
Noting $\omega = 2\pi/s$, the harmonic series of frequency $\omega$ represents a series that repeats itself every $s$ periods.
For example, for a monthly series ($s=12$ observations per year), seasonal movements are those that repeat every year: they are therefore associated with frequencies $2\pi/12$ (annual periodicity), $2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5$.
In this paper, we consider that the trend-cycle is associated with frequencies in the interval $[0, 2\pi/12]$, i.e. movements recurring at least every 12 months.
Even if different frequencies are sometimes used (e.g. $[0, 2\pi/36]$ to consider only cycles of at least 36 months), this has no impact on the results of the study.
The other frequencies, $[2\pi/12, \pi]$ are associated with the irregular component (undesirable oscillations).

@fig-graphsmusgrave shows the gain and phase shift function for the asymmetric Musgrave filter (see @sec-lppasymf) often used for real-time trend-cycle estimation (i.e. when no point in the future is known).
The gain function is greater than 1 on the frequencies associated with the trend-cycle ($[0, 2\pi/12]$): this means that the trend-cycle is well preserved and that short cycles of 1 to 2 years ($[2\pi/24,2\pi/12]$) are even amplified.
At other frequencies, the gain function is less than 1, but always positive: this means that the series smoothed by this moving average will always contain noise, even if it is attenuated.
Analysis of the phase shift shows that the shorter the cycles, the greater the phase shift: this means that on series smoothed by this moving average, turning points could be detected at the wrong date.

@@

## Trend-cycle estimates and moving average

Les méthodes présentées dans cette étude permettent de lisser les séries afin d'extraire la composante tendance-cycle pour faciliter l'analyse des retournements conjoncturels dans le cycle classique (également appelé cycle des affaires).
On ne cherche donc pas à estimer séparément la tendance (qui représente les évolutions de long terme) et le cycle (qui représente les évolutions cycliques autour de la tendance) puisque ces composantes peuvent être difficiles à séparer (quelle définition prendre pour distinguer les cycles courts et des cycles longs ?).
Par ailleurs, la décomposition entre tendance et cycle, associée à des méthodes de filtrage de type Hodrick-Prescott ou Baxter-King, sont plutôt utilisées pour analyser les points de retournement dans le cycle de croissance (voir @ferrara2009caracterisationcycles pour une description des différents cycles économiques).
Ces méthodes de décomposition tendance et cycle nécessitent d'avoir des séries longues (afin de distinguer cycles courts et tendance de long terme) alors que les méthodes utilisées dans cet article utilisent peu d'observations (en général 13 pour des séries mensuelles).

@@

In this paper, we assume that our initial series $y_t$ is seasonally adjusted and can be written as the sum of a trend-cycle, $TC_t$, and an irregular component, $\varepsilon_t$:
$$
y_t=TC_t+\varepsilon_t.
$$
The aim will be to build moving averages that best preserve the trend-cycle ($M_{\boldsymbol\theta} (TC_t)\simeq TC_t$).

@@

### Asymmetric moving averages and forecasts {#sec-mmetprev}

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period.
A similar approach is used in the X-13ARIMA-SEATS seasonal adjustment method: the series is extend by one year (by default) with an ARIMA model to minimise the revisions associated to asymmetric filters

@@

Various estimation methods can be used to derive symmetric and asymmetric moving averages.  
@GrayThomson1996 propose a complete statistical framework that makes it possible, in particular, to model the error in approximating the trend by local polynomials.
However, as the specification of this error is generally complex, simpler models may be preferred, such as that of @proietti2008.  
Finally, @dagumbianconcini2008 propose a similar modelling of the trend-cycle but using the theory of Hilbert spaces with reproducing kernels for estimation, which has the particular advantage of facilitating the calculation of different moving averages at different time frequencies,
this method can be used in R with the function `rjd3filters::rkhs_filter()`.

## Symmetric moving averages and local polynomial regression

@@

As mentioned in @sec-mmetprev, for real-time estimation, several approaches can be used:

@@

Rewriting @eq-lpp:
$$
\boldsymbol y=\begin{pmatrix}\boldsymbol U &\boldsymbol Z\end{pmatrix}
\begin{pmatrix}\boldsymbol \gamma \\ \boldsymbol \delta\end{pmatrix}+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
$$ {#eq-lpgeneralmodel}
where $[\boldsymbol U,\boldsymbol Z]$ is of full rank and forms a subset of the columns of $X.$
Defining the variance error as $\boldsymbol D = \sigma^2\boldsymbol K^{-1}$ (to directly take into account the weights associated to the observations) and with $[\boldsymbol U,\boldsymbol Z] = \boldsymbol X$ we this find the model associated to symmetric filters.
The objective is to find an asymmetric filter $\boldsymbol v$ which uses $q$ points in the future and minimises the mean square error of revision (to the symmetric filter $\boldsymbol \theta$) under certain (polynomial) constraints.
The matrices $\boldsymbol y$, $\boldsymbol U$, $\boldsymbol Z$ and $\boldsymbol \theta$ are partitioned as follows:
$$
\boldsymbol y = \begin{pmatrix} \boldsymbol y_p \\ \boldsymbol y_f \end{pmatrix}, \quad
\boldsymbol U = \begin{pmatrix} \boldsymbol U_p \\ \boldsymbol U_f \end{pmatrix}, \quad  
\boldsymbol Z = \begin{pmatrix} \boldsymbol Z_p \\ \boldsymbol Z_f \end{pmatrix}, \quad 
\boldsymbol \theta = \begin{pmatrix} \boldsymbol \theta_p \\ \boldsymbol \theta_f \end{pmatrix},
$$
where $\boldsymbol y_p$ is a matrix $(h+q+1)\times 1$ which denotes the set of available observations (from $y_{t-h}$ to $y_{t+q}$) and $\boldsymbol U$, $\boldsymbol Z$ and $\boldsymbol \theta$ are partitioned in the same way.
The constraints are defined as $\transp{\boldsymbol U_p}\boldsymbol v=\transp{\boldsymbol U}\boldsymbol \theta$: they represents the polynomial preservation constraints we want to impose on the asymmetric filter.
@proietti2008 show that the problem is equivalent to finding $v$ which minimises:
$$
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{\transp{(\boldsymbol v-\boldsymbol \theta_{p})}\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \transp{\boldsymbol \theta_{f}}\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\transp{\boldsymbol \delta}(\transp{\boldsymbol Z_{p}}\boldsymbol v-\transp{\boldsymbol Z}\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\transp{\boldsymbol l}(\transp{\boldsymbol U_{p}}\boldsymbol v-\transp{\boldsymbol U}\boldsymbol \theta)}_{\text{constraints}}.
$$ {#eq-lppasym}
where $\boldsymbol l$ is a vector of Lagrange multipliers.

When $\boldsymbol U=\boldsymbol X$ (and then $\boldsymbol Z = \boldsymbol 0$), the constraint is equivalent to preserving polynomials of degree $d$ and we find asymmetric direct filters (DAF) when $\boldsymbol D=\boldsymbol K^{-1}$.

@@

- The parameter $\delta$ can be estimated by moving average from @eq-mmsym. 
For example, for the LC method we can use the moving average $\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}$ to obtain a local estimate of the slope and for the QL method we can use $\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}$ to obtain a local estimate of the concavity. 
The DAF method then simply allows us to calculate the associated asymmetric moving averages.  
Although a moving average of different length to that used for estimating the trend could be considered, this seems to degrade the results in terms of phase shift (using the same methodology as in @sec-comparison).
Furthermore, for the construction of moving averages, the trend can be modelled as being locally of degree 2 or 3 (this has no impact on the final estimate of concavity).
Here, we have chosen to model a trend of degree 2: this slightly reduces the phase shift (see Supplemental material) but slightly increases the revisions linked to the first estimate of the trend-cycle. 
@fig-mmpenteconcac shows the moving averages used.

@@

In the empirical applications of @sec-comparison, the final local parametrisation is obtained by estimating $\delta$ using all the data (i.e., using the symmetric filters shown in @fig-mmpenteconcac), while maintaining a real-time estimate of $\sigma^2$.
@fig-mmpenteconcac-ex shows an example of the comparison of estimates of the ratio $|\delta_1/\sigma|$ with a global estimator (IC ratio) and two local parametrisations:

@@

The turning points are clearly detected by the local estimators, but there is much more variance in the estimate of $|\delta_1/\sigma|$ in the real-time estimate.
This will lead to another source of revisions in the intermediate estimates.

@@

@@

The different methods are compared on simulated and real data. 
For all series, a symmetric 13-term filter is used: we then assume than the bandwidth is fixed, as in the seasonal adjustement method X-11.
A nearest neighbour bandwidth is also tested (13-term asymmetric filters: real-time estimates uses observation between $y_{t-12}$ and $y_{t}$, the second asymmetric filters uses obversations between $y_{t-11}$ and $y_{t+1}$, etc.) but with no improvement in the results (see supplemental material).
More complexe methods to locally select bandwidth, like the one proposed by @fan1992variable, were not tested.
All the methods to create asymmetric filters are also compared with estimates obtained by extending the series with an ARIMA model, then applying a 13-term symmetric Henderson filter.
The ARIMA model is determined automatically, using @autoarima algorithm (function `forecast::auto.arima()`), using no seasonal lag (the series being seasonally adjusted) and no external variables (such as external regressors for correction of atypical points).

@@

@@

1. Computation of the phase shift in the detection of turning points. The definition of @Zellner1991 is used to determine the turning points:  
    - An upturn occurs when the economy moves from a phase of recession to a phase of expansion. 
    This is the case at date  $t$ when $y_{t-3}\geq y_{t-2}\geq y_{t-1}<y_t\leq y_{t+1}$.  
    - A downturn occurs when the economy moves from a phase of expansion to a phase of recession.
This is the case at date  $t$ when $y_{t-3}\leq y_{t-2}\leq y_{t-1}>y_t\geq y_{t+1}$.  
    It thus takes at least 2 months to detect a turning point.  
    The phase shift is often defined as the number of months required to detect the right turning point.
    Here we use a slightly modified criterion: the phase shift is defined as the number of months needed to detect the right turning point without any future revision.
    Indeed, it can happen that the right turning point is detected by asymmetric filters but is not detected by the final estimate using a symmetric filter (this is the case for 41 reversal points out of the 9 series with asymmetric Musgrave filters) or that there are revisions in successive estimates (this is the case for 7 turning points out of the 9 series with asymmetric Musgrave filters).
  Finally, relatively few turning points are detected at the right date with the final estimate.
  With the 13-term Henderson filter, 18 are correctly detected in series with low variability (out of 57 possible), 11 in series with medium variability and 12 in series with high variability.

2. The average of the relative deviations between to the last estimate (comparison of the $q$^th^ estimate and the last estimate):
$$
MAE_{fe}(q)=\mathbb E\left[
\left|\frac{
y_{t|t+q} -  y_{t|last}
}{
 y_{t|last}
}\right|
\right].
$$
3. The average of the relative deviations between two consecutive estimates (the $q$^th^ estimate and the $q+1$^th^ estimate):
$$
MAE_{ce}(q)=\mathbb E\left[
\left|\frac{
y_{t|t+q} - y_{t|t+q+1}
}{
y_{t|t+q+1}
}\right|
\right].
$$

@@

Extending the series using an ARIMA model gives revisions with the latest estimates of the same order of magnitude as the LC filter, but slightly larger revisions between consecutive estimates, particularly between the fourth and fifth estimates (as might be expected, as highlighted in @sec-mmetprev).

::: {#tbl-simulrev}
```{r}
#| echo: false
rev_table <- readRDS("data/simulations_revisions.RDS")
pack_row_index = c("$MAE_{fe}(q) = \\mathbb E\\\\left[\\\\left|(y_{t|t+q} -  y_{t|last})/y_{t|last}\\\\right|\\\\right]$" = nrow(rev_table) / 2,
                   "$MAE_{ce}(q)=\\mathbb E\\\\left[
\\\\left|(y_{t|t+q} - y_{t|t+q+1})/y_{t|t+q+1}\\\\right|
\\\\right]$" = nrow(rev_table) / 2)
rev_table  %>%
  kable(format.args = list(digits = 2,
                           decimal.mark = "."),
        align = "c", booktabs = T, row.names = FALSE, 
        escape = FALSE,) %>%  
  kable_styling(latex_options=c(#"striped",  
    "hold_position")) %>% 
  pack_rows(index = pack_row_index, escape = FALSE) # %>%
    # add_footnote_kable(stop_centering = TRUE)
```
Lecture: the estimates for $q=0$ correspond to the first estimates of the trend-cycle (real-time estimates when 0 point in the future is known), $q=1$ correspond to the second estimates of the trend-cycle (when 1 point in the future is known).
Since the final estimates are obtain using a symmetric filter of bandwidth 6, $q=6$ corresponds to the final estimates of the trend-cycle (when 6 points in the future are known).
$MAE_{fe}(0)$ compares the revision between the first estimate ($q=0$) and the last estimate ($q=6$) and $MAE_{ce}(0)$ compares the revision between the first estimate ($q=0$) and the second estimate ($q=1$).

@@

\appendix
\newpage

# Coefficients, gain and phase shift functions {#sec-an-cof}

>>>>

:::: {.abstract}
This paper studies and compares real-time estimates of the trend-cycle component with moving averages based on local polynomial regression.
In particular, this theory allows us to reproduce Henderson's symmetric and Musgrave's asymmetric filters used in the X-13ARIMA-SEATS seasonal adjustment algorithm.
This paper proposes two extensions of local polynomial filters for real-time trend-cycle estimates (for the last estimates): first including a timeliness criterion to minimise the phase shift;
second, with procedure for parametrising asymmetric filters locally While they are generally parametrised globally, which can be suboptimal around turning points.
An empirical comparison, based on simulated and real data, shows that modelling polynomial trends that are too complex introduces more revisions without reducing the phase shift, and that local parametrisation reduces the delay in detecting turning points and reduces revisions.
The paper also shows how these results can be easily reproduced using the R package `rjd3filters` dedicated to the manipulation of moving averages.

@@

Using local polynomial regression, @proietti2008 developed a general class of symmetric and asymmetric moving averages.
In particular, it becomes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
The aim of this study is to propose two extensions to the @proietti2008 class of filters in order to two drawbacks of those methods.
Firstly,  adding, in the optimisation process, a timeliness criterin to directly control the phase shift (i.e. the delay in detecting turning points).
Secondly, calibrating asymmetric filter locally, while they are generally calibrated globally  using thus assumptions that may be wrong locally.
Those extensions are implemented in the statistical software R [@logicielr] throw the `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and can therefore be easily used.
All the code associated to this paper is available at <https://github.com/XXXX> (anonymized linked before the manuscript is accepted).

@@

The basic assumption  used in  time series decomposition methods is that the input observed time series, $y_t$ can be decomposed into a signal component $\mu_t$ and a an erratic component $\varepsilon_t$ (called irregular):
$$
f(y_t)=\mu_t+\varepsilon_t
$$
where $f$ denotes some appropriate transformation (usually logarithmic or no transformation).
To simplify further notations, $y_t$ will denote the transformed observed series.
The noise component $\varepsilon_t$ is usually assumed to be a white noise.
Assuming that the input time series is seasonally adjusted (or without seasonality), the signal $\mu_t$ represents the trend and cycle components, here estimated jointly and called trend-cycle $TC_t$.
This component can be locally approximated by a polynomial degree (see @sec-nonparamreg):
$$
\mu_t = \sum_{j=0}^d\beta_jt^j+\xi_t
$$
with $\xi_t$ a stochastic process uncorrelated with $\varepsilon_t$.
Event if some papers model $\xi_t$ and $\varepsilon_t$ separately [see for example @GrayThomson2002], an usual assumption, adopted in this paper, is to is to gather $\xi_t$ and $\varepsilon_t$.
Thus, the trend-cycle $TC_t$ is considered as deterministic and modelled as a polynomial trend of degree $d$.
The coefficients $(\beta_0,\dots,\beta_k)$ can be estimated by weighted least squares.
The estimate $\hat \beta_0$ provides the trend-cycle estimate $\hat TC_t$ and it can be shown that this equivalent to apply of moving average (see @sec-nonparamreg).
The goal of this paper is to present two new methods to separate the trend-cycle component from the noise component in real-time (i.e. when no future point is known), using moving averages build on local polynomial smoothing techniques.

@@

Fourier decomposition allows us to analyze any time series as a sum of harmonic series, and each component (trend, cycle, seasonal, irregular) is associated with a set of frequencies.
Noting $\omega = 2\pi/s$, the harmonic series of frequency $\omega$ represents a series that repeats itself every $s$ periods.
For example, for a monthly series ($s=12$ observations per year), seasonal movements are those that repeat every year: they are therefore associated with frequencies $2\pi/12$ (annual periodicity), $2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5$.
In this paper, we consider that the trend-cycle is associated with frequencies in the interval $[0, 2\pi/12]$, i.e. movements recurring at least every 12 months.
Even if different frequencies are sometimes used (e.g. $[0, 2\pi/36]$ to consider only cycles of at least 36 months), this has no impact on the results of the study.
The other frequencies, $[2\pi/12, \pi]$ are associated with the irregular component.

@Fig-graphsmusgrave shows the gain and phase shift function for the asymmetric Musgrave filter (see @sec-lppasymf) often used for real-time trend-cycle estimation (i.e. when no point in the future is known).
The gain function is greater than 1 on the frequencies associated with the trend-cycle ($[0, 2\pi/12]$): this means that the trend-cycle is well preserved and that short cycles of 1 to 2 years ($[2\pi/24,2\pi/12]$) are even amplified.
At other frequencies, the gain function is less than 1, but always positive: this means that the series smoothed by this moving average will always contain noise, even if it is attenuated.
Analysis of the phase shift shows that the shorter the cycles, the greater the phase shift: this means that on series smoothed by this moving average, turning points could be detected at the wrong date.

@@

@@

In this paper, we assume that our initial series $y_t$ is seasonally adjusted and can be written as the sum of a trend-cycle, $TC_t$, and an irregular (noise) component, $\varepsilon_t$:
$$
y_t=TC_t+\varepsilon_t.
$$
The aim will be to build moving averages that best preserve the trend-cycle ($M_{\boldsymbol\theta} (TC_t)\simeq TC_t$).

@@

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period.
A similar approach is used in the X-13ARIMA-SEATS seasonal adjustment method: the series is extend by one year (by default) with an ARIMA model to minimise the revisions associated to asymmetric filters.
Since the final filter used for the seasonal adjustment extraction is much longer than one year (in most of the cases, for monthly series, the bandwidth is 78), the input series is just partially extended (and asymmetric filters are still used) to prevent from instability over long periods (e.g., outliers or model shifts).

@@

Various estimation methods can be used to derive symmetric and asymmetric moving averages.  
@GrayThomson1996 propose a complete statistical framework that makes it possible, in particular, to model the error in approximating the trend by local polynomials.
However, as the specification of this error is generally complex, simpler models may be preferred, such as that of @proietti2008.  
Finally, @dagumbianconcini2008 propose a similar modelling of the trend-cycle but using the theory of Hilbert spaces with reproducing kernels for estimation, which has the particular advantage of facilitating the calculation of different moving averages at different time frequencies.
See @inseeDTM202401 for a more detailed comparison of the different recent methods for trend-cycle extraction included in the `rjd3filters` package

In this paper we will focus on @proietti2008 approach. 
@Sec-sym-lp and @sec-lppasymf describes their approach to build symmetric moving averages (used for the final estimates of the trend-cycle component) and asymmetric moving averages (used for real-time estimates).
This paper proposed two extensions of their approach to build asymetric moving averages: a first one adding a criteria to control the phase shift (@sec-localic), not used in the simulation (@sec-comparison) but which could be used in future studied; a second one using a local parameterisation of a parameter usually parameterised globally (@sec-lptimeliness), which is used in the simulation.

## Symmetric moving averages and local polynomial regression {#sec-sym-lp}

@@

As mentioned in @sec-mmasym, for real-time estimation, several approaches can be used:

@@

Rewriting @eq-lpp:
$$
\boldsymbol y=\begin{pmatrix}\boldsymbol U &\boldsymbol Z\end{pmatrix}
\begin{pmatrix}\boldsymbol \gamma \\ \boldsymbol \delta\end{pmatrix}+\boldsymbol \varepsilon,\quad
\boldsymbol \varepsilon\sim\mathcal{N}(0,\boldsymbol D).
$$ {#eq-lpgeneralmodel}
where $[\boldsymbol U,\boldsymbol Z]$ is of full rank and forms a subset of the columns of $X.$
Defining the variance error as $\boldsymbol D = \sigma^2\boldsymbol K^{-1}$ (to directly take into account the weights associated to the observations) and with $[\boldsymbol U,\boldsymbol Z] = \boldsymbol X$ we thus find the model associated to symmetric filters.
The objective is to find an asymmetric filter $\boldsymbol v$ which uses $q$ points in the future and minimises the mean square error of revision (to the symmetric filter $\boldsymbol \theta$) under certain (polynomial) constraints.
The matrices $\boldsymbol y$, $\boldsymbol U$, $\boldsymbol Z$ and $\boldsymbol \theta$ are partitioned as follows:
$$
\boldsymbol y = \begin{pmatrix} \boldsymbol y_p \\ \boldsymbol y_f \end{pmatrix}, \quad
\boldsymbol U = \begin{pmatrix} \boldsymbol U_p \\ \boldsymbol U_f \end{pmatrix}, \quad  
\boldsymbol Z = \begin{pmatrix} \boldsymbol Z_p \\ \boldsymbol Z_f \end{pmatrix}, \quad 
\boldsymbol \theta = \begin{pmatrix} \boldsymbol \theta_p \\ \boldsymbol \theta_f \end{pmatrix},
$$
where $\boldsymbol y_p$ is a matrix $(h+q+1)\times 1$ which denotes the set of available observations (from $y_{t-h}$ to $y_{t+q}$) and $\boldsymbol U$, $\boldsymbol Z$ and $\boldsymbol \theta$ are partitioned in the same way.
The constraints are defined as $\transp{\boldsymbol U_p}\boldsymbol v=\transp{\boldsymbol U}\boldsymbol \theta$: they represents the polynomial preservation constraints we want to impose on the asymmetric filter.
@proietti2008 show that the problem is equivalent to finding $v$ which minimises:
$$
\varphi(\boldsymbol v)=
\underbrace{
  \underbrace{\transp{(\boldsymbol v-\boldsymbol \theta_{p})}\boldsymbol D_{p}(\boldsymbol v-\boldsymbol \theta_{p})+
  \transp{\boldsymbol \theta_{f}}\boldsymbol D_{f}\boldsymbol \theta_{f}}_\text{revision error variance}+
  \underbrace{[\transp{\boldsymbol \delta}(\transp{\boldsymbol Z_{p}}\boldsymbol v-\transp{\boldsymbol Z}\boldsymbol \theta)]^{2}}_{bias^2}
}_\text{mean square revision error}+
\underbrace{2\transp{\boldsymbol l}(\transp{\boldsymbol U_{p}}\boldsymbol v-\transp{\boldsymbol U}\boldsymbol \theta)}_{\text{constraints}}.
$$ {#eq-lppasym}
where $\boldsymbol l$ is a vector of Lagrange multipliers.

When $\boldsymbol U=\boldsymbol X$ (and then $\boldsymbol Z = \boldsymbol 0$), the constraint is equivalent to preserving polynomials of degree $d$ and we find asymmetric direct filters (DAF) when $\boldsymbol D=\sigma^2\boldsymbol K^{-1}$.

@@

- The parameter $\delta$ can be estimated by moving average from @eq-mmsym. 
For example, for the LC method we can use the moving average $\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}$ to obtain a local estimate of the slope and for the QL method we can use $\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}$ to obtain a local estimate of the concavity. 
The DAF method then simply allows us to calculate the associated asymmetric moving averages.  
Although a moving average of different length to that used for estimating the trend could be considered, this seems to degrade the results in terms of phase shift (using the same methodology as in @sec-comparison).
Furthermore, for the construction of moving averages, the trend can be modelled as being locally of degree 2 or 3 (this has no impact on the final estimate of concavity).
In this paper, we have chosen to model a trend of degree 2: this slightly reduces the phase shift (see Supplemental material) but slightly increases the revisions linked to the first estimate of the trend-cycle. 
@fig-mmpenteconcac shows the moving averages used.

@@

To distinguish the gain from the local parametrisation of the noise biased associated to the real-time estimates of the slope and concavity, in the empirical applications of @sec-comparison we also compares the results to the final local parametrisation obtained by estimating $\delta$ using all the data (i.e., using the symmetric filters shown in @fig-mmpenteconcac), while maintaining a real-time estimate of $\sigma^2$.
@fig-mmpenteconcac-ex shows an example of the comparison of estimates of the ratio $|\delta_1/\sigma|$ with a global estimator (IC ratio) and two local parametrisations:

@@

The turning points are clearly detected by the local estimators (changement in the slope), when $|\delta_1/\sigma|$ is estimated in the real-time estimate.
However, the real-time local estimates of $|\delta_1/\sigma|$ are noisy: the varability of this estimates, used to build asymmetric filters, will then lead to another source of revisions in the intermediate estimates.

@@

There is no function in `rjd3filters` to directly compute those moving averages but they can be easily computed using matrix computation formula and applied to the series rjd3filters`.

@@

The different methods are compared on simulated and real data. 
For all series, a symmetric 13-term filter is used: we then assume than the bandwidth is fixed, as in the seasonal adjustement method X-11.
A nearest neighbour bandwidth is also tested (13-term asymmetric filters: real-time estimates uses observation between $y_{t-12}$ and $y_{t}$, the second asymmetric filters uses obversations between $y_{t-11}$ and $y_{t+1}$, etc.) but with no improvement in the results (see supplemental material).
More complexe methods to locally select bandwidth, like the one proposed by @fan1992variable, were not tested.
All the methods to create asymmetric filters are also compared with estimates obtained by extending the series with an ARIMA model, then applying a 13-term symmetric Henderson filter.
The ARIMA model is determined automatically, using @autoarima algorithm (function `forecast::auto.arima()`) on the last 12 years, with no seasonal lag (the series being seasonally adjusted) and no external variables (such as external regressors for correction of atypical points).

@@

The series associa

@@

1. Computation of the phase shift in the detection of turning points. 
In this paper, we focus on turning points associated to business cycle: it is defined as the succession of phases of economic recession and expansion, delimited by peaks (highest level of activity) and troughs (lowest level of activity), see for example @ferrara for a description of the different economic cycles.
In this paper, following @Zellner1991, we used an accepted definition for turning-points:  
    - An upturn occurs when the economy moves from a phase of recession to a phase of expansion. 
    This is the case at date  $t$ when $TC_{t-3}\geq TC_{t-2}\geq TC_{t-1}<TC_t\leq TC_{t+1}$.  
    - A downturn occurs when the economy moves from a phase of expansion to a phase of recession.
This is the case at date  $t$ when $TC_{t-3}\leq TC_{t-2}\leq TC_{t-1}>TC_t\geq TC_{t+1}$.

  Lets denote $TC_{t|t'}$ the estimate of the trend-cycle at date $t$ using the data up to date $t'$.
  The phase shift is often defined as the number of months required to detect the right turning point: it would then be equal to two if, in the case of a downturn,  $TC_{t-3|t+1}\leq TC_{t-2|t+1}\leq TC_{t-1|t+1}>TC_{t|t+1}\geq TC_{t+1|t+1}$ (two observations, at dates $t$ and $t+1$, are needed to qualify the date $t$ as turning point).
  Note that, in that case, the phase shift could be equivalently set to 1 (only one observation after $t$ is needed to define $t$ as a turning point), without any difference on the comparison of the different methods.\
  In this paper we use a slightly modified criterion: the phase shift is defined as the number of months needed to detect the right turning point without any future revision.
  Thus, in the case of a downturn, the phase shift is two if $TC_{t-3|t+1}\leq TC_{t-2|t+1}\leq TC_{t-1|t+1}>TC_{t|t+1}\geq TC_{t+1|t+1}$ and, for all dates $t'$ higher than $t+1$: $TC_{t-3|t'}\leq TC_{t-2|t'}\leq TC_{t-1|t'}>TC_{t|t'}\geq TC_{t+1|t'}$.
Since a 13-term Henderson filter is used for the final estimates of the trend-cycle, the phase shift is at most height (the final estimate of $TC_{t+1}$ is compute a the date $t+7$).
  This definition is used because it can happen that the right turning point is detected by asymmetric filters but is not detected by the final estimate using a symmetric filter (this is the case for 41 reversal points out of the 9 series with asymmetric Musgrave filters) or that there are revisions in successive estimates (this is the case for 7 turning points out of the 9 series with asymmetric Musgrave filters).
  Finally, relatively few turning points are detected at the right date with the final estimate.
  With the 13-term Henderson filter, 18 are correctly detected in series with low variability (out of 57 possible), 11 in series with medium variability and 12 in series with high variability.

2. The average of the relative deviations between to the last estimate (comparison of the $q$^th^ estimate and the last estimate):
$$
MAE_{fe}(q)=\mathbb E\left[
\left|\frac{
TC_{t|t+q} -  TC_{t|last}
}{
 TC_{t|last}
}\right|
\right].
$$

3. The average of the relative deviations between two consecutive estimates (the $q$^th^ estimate and the $q+1$^th^ estimate):
$$
MAE_{ce}(q)=\mathbb E\left[
\left|\frac{
TC_{t|t+q} - TC_{t|t+q+1}
}{
TC_{t|t+q+1}
}\right|
\right].
$$

@@

Extending the series using an ARIMA model gives revisions with the latest estimates of the same order of magnitude as the LC filter, but slightly larger revisions between consecutive estimates, particularly between the fourth and fifth estimates (as might be expected, as highlighted in @sec-mmasym).

::: {#tbl-simulrev}
```{r}
#| echo: false
rev_table <- readRDS("data/simulations_revisions.RDS")
pack_row_index = c("$MAE_{fe}(q) = \\mathbb E\\\\left[\\\\left|(TC_{t|t+q} -  TC_{t|last})/TC_{t|last}\\\\right|\\\\right]$" = nrow(rev_table) / 2,
                   "$MAE_{ce}(q)=\\mathbb E\\\\left[
\\\\left|(TC_{t|t+q} - TC_{t|t+q+1})/TC_{t|t+q+1}\\\\right|
\\\\right]$" = nrow(rev_table) / 2)
rev_table  %>%
  kable(format.args = list(digits = 2,
                           decimal.mark = "."),
        align = "c", booktabs = T, row.names = FALSE, 
        escape = FALSE,) %>%  
  kable_styling(latex_options=c(#"striped",  
    "hold_position")) %>% 
  pack_rows(index = pack_row_index, escape = FALSE) # %>%
    # add_footnote_kable(stop_centering = TRUE)
```
Lecture: the estimates for $q=0$ correspond to the first estimates of the trend-cycle (real-time estimates when 0 point in the future is known), $q=1$ correspond to the second estimates of the trend-cycle (when 1 point in the future is known).
Since the final estimates are obtain using a symmetric filter of bandwidth 6, $q=6$ corresponds to the final estimates of the trend-cycle (when 6 points in the future are known).
$MAE_{fe}(0)$ compares the revision between the first estimate ($q=0$) and the last estimate ($q=6$) and $MAE_{ce}(0)$ compares the revision between the first estimate ($q=0$) and the second estimate ($q=1$).

@@

<!-- \appendix -->
<!-- \newpage -->

<!-- # Coefficients, gain and phase shift functions {#sec-an-cof} -->
